---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.width = 10,
  fig.height = 10 / 1.618
)
```

# zibas

<!-- badges: start -->
<!-- badges: end -->

The goal of `zibas` is to make it easy to consistently create beautiful graphs.

The inspiration for this package comes from the brilliant book *Storytelling with Data* by Cole Nussbaumer Knaflic. 

## Installation

You can install the development version of zibas from [GitHub](https://github.com/) with:

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("datr-studio/zibas")
```


## Usage

```{r }
library(zibas)
library(ggplot2)
```

Using `zibas` is simple: just add `theme_ziba()` to any ggplot. 

```{r }
ggplot(mtcars, aes(hp, mpg, color = cyl, group = cyl)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  labs(
    x = "Horsepower", y = "Miles / Gallon",
    title = "A meaningless graph",
    subtitle = "Only for the sake of illustration",
    color = "Cylinders"
  ) +
  theme_ziba()
```

### Ridge plots

If however, you want to do a ridge plot, `theme_ziba_ridges()` is recommended, for subtle shifts in the axis location. 

```{r }
library(ggridges)
ggplot(lincoln_weather, aes(x = `Mean Temperature [F]`, y = `Month`, fill = stat(x))) +
  geom_density_ridges_gradient(scale = 3, rel_min_height = 0.01) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)) +
  scale_fill_viridis_c(name = "Temp. [F]", option = "C") +
  coord_cartesian(clip = "off") +
  labs(title = "Temperatures in Lincoln NE in 2016") +
  theme_ziba_ridges()
```

### Other goodies

In addition to the themes, `zibas` also provides a standard set of colours. Following the recommendations of *Storytelling with data*, a single blue, red, and two grays are provided, using `zibablue()`, `zibared()`, `zibagray()`, and `zibadarkgray()`. 

A gradient function also exists using `ziba_gradient()`, which can return n colours in the blue spectrum. This is based on the Brewer Palette's blues (`RColorBrewer`), but expands it to an arbitrary number (whereas the original is capped at 9 shades).

To apply this directly to a ggplot, simply add `scale_fill_ziba_blue()` or `scale_colour_ziba_blue()` as you would any other colour scale. 